Associative Data Structures for Website Filtering

### 2014-04-17 paper/paper.tex
research description
ik heb dit gemerged met het implementation deel wat er al stond, er zat
erg veel overlap in

    \begin{quotation}How does the number of entries influence the performance of various associative data structures?\end{quotation}

@@

    \begin{quotation}How does the complexity of the key influence the preformance of various associative data structures?\end{quotation}

    In the following paper, we will attempt to answer these questions. The next section will provide details
    about our research plan and the scopes of our research. The section thereafter is about the implementation
    of our setup in C++. Next, we will state our results, after which we will discuss set results and provide
    several conclusions.    
    %We did research about what data structure could best be used to represent a blacklist in a 
    %web-filter application.  We compared the insertion speed, query speed, and memory usage of three
    %data structures: the binary search tree, the hash table, and the skip list.  We did this because
    %we really liked these three structures. 
    \section{Implementation}
    \subsubsection*{Datastructures}

@@

    \subsubsection*{Data}
    For our data, we took the system's dictionary file and the list of top level domains from Wikipedia
    and combined these to generate a list of items in the form \texttt{www.\$word.\$tld}, where
    \texttt{\$word} is one of words from the the dictionary and \texttt{\$tld} is a top level domain.  Only
    words consisting of the lowercase letters \texttt{a} through \texttt{z} were used.  Constraining the
    words to consist of 8 to 12 characters and limiting the top-level domains to exactly two letters, 
    all possible combinations were generated.  For the full paths, a number of domains were selected
    and each was appended a random alphanumeric string of eighty characters.  The exact implementation
    can be viewed in the sourcecode\footnote{ref to apendix or code dump}.

>>>>

    \emph{How does the number of entries influence the performance of various associative data structures?}

@@

    \emph{How does the complexity of the key influence the preformance of various associative data structures?}

    In this paper, we will attempt to answer these questions. The next section will provide details
    about our research plan (based largely on our original plan) and the implementation of our setup in C++. 	 
    Next, we will state our results, after which we will discuss set results and provide several conclusions.    
    %We did research about what data structure could best be used to represent a blacklist in a 
    %web-filter application.  We compared the insertion speed, query speed, and memory usage of three
    %data structures: the binary search tree, the hash table, and the skip list.  We did this because
    %we really liked these three structures.

    \section{Research description}

    \subsubsection*{Scope and assumptions}

    We make several assumptions for our research.

	Firstly we plan on only working with datasets that are certain to fit into the main memory of our machine. We intend to 
    purely examine the relative speed and memory-efficiency of the different data structures. Using datasets larger than 
    memory will cause regular lookups to the harddrive, which we assume would skew our results.

    In order to make the measurements more predictable, we will always ensure that insertions are only performed with 
    non-existent keys. The alternative would make either the memory usage or number of insertions non-deterministic, which 
    could cause inaccuracies in measurement. Similarly, we require that all queries be performed on existing keys.

	To mimic real usage, we will insert and then access the keys in an arbitrary order.  However, we will keep the order consistent 
    between tests on different data structures.  Together this will minimize any bias related to any kind of order-dependent 
    performance, which would likely be an advantage specific to the implementation, not to the data structure. We will 
    generate the order for both lookup and insertion by shuffling the dataset we chose for the specific test. This means that 
    orders will not be persistent between different data set sizes; however, we do not expect this to be significant.

	We realize that methods to measure the amount of time required for actions will themselves need time. We will however 
    use the same time-measuring method for all data structures, so we can still use the results to compare the different 
    data structures.

    \subsubsection*{Datastructures}

@@

    \subsubsection*{Data}
    For our data, we used datasets containing $2^x$ elements with $x$ an integer such that $8 < x < 21$. Thus we have 
    twelve different dataset sizes. we took the system's dictionary file and the list of top level domains from Wikipedia 
    and combined these to generate a list of items in the form \texttt{www.\$word.\$tld}, where \texttt{\$word} is one 
    of words from the the dictionary and \texttt{\$tld} is a top level domain.  Only words consisting of the lowercase 
    letters \texttt{a} through \texttt{z} were used. Constraining the words to consist of 8 to 12 characters and limiting 
    the top-level domains to exactly two letters, all possible combinations were generated.  For the full paths, a number 
    of domains were selected and each was appended a random alphanumeric string of eighty characters.  Finally, for the 
    third type of key, an IP address, we used 32 bit integers. The exact implementation can be viewed in the 
    sourcecode\footnote{ref to apendix or code dump}.
